---
title: 'R Notebook: colors'
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 4
    fig_caption: true
    number_sections: true 
---

# Setup

## include-setup.R

This one file has all the basic functions we need to load more functions.

### source setup
```{r}
github.monte.raw = "https://raw.githubusercontent.com/MonteShaffer/";
include.setup = paste0(github.monte.raw, "humanVerse/main/include.setup.R");
source(include.setup);
```

### Custom Sourcing

#### TEMP folder
```{r}
getSourceLocation();
```

#### source (humanVerse/R)
```{r}
github.monte.http = "https://github.com/MonteShaffer/";
######## we will parse this page to get a list of the .R functions to include ########
github.monte.humanVerse = paste0(github.monte.http, "humanVerse/tree/main/humanVerse/R/"); 

######## you can pass flag `force.download = TRUE` if you want to make certain it is not coming from cache ########

###### R::humanVerse #####
includeGithubFolder(github.monte.humanVerse, force.download = TRUE); 
```

#### source (humanVerse/misc)
```{r}
######## we will parse this page to get a list of the .R functions to include ########
github.monte.misc = paste0(github.monte.http, "humanVerse/tree/main/misc/"); 

######## you can pass flag `force.download = TRUE` if you want to make certain it is not coming from cache ########

###### R::humanVerse #####
includeGithubFolder(github.monte.misc, force.download = TRUE);
```


# Color Theory

Color is an important aspect of visualization and storytelling with data.  As I am not an "artist", I have to rely on mathematics to generate colors that look nice together.

## colors.mshaffer.com
Here was a color tool I developed in 2007:

<https://colors.mshaffer.com/>

<https://colors.mshaffer.com/?debug=monte>

## Color formats

The primary color scheme we use today is called "hexadecimal" colors.  It is a form of "RGB" color that is converted to a string.  RGB stands for (R)ed, (G)reen, (B)lue where each value can be [0-255] which converted to hexadecimal as a string is "00" to "FF".

#### === War-story Tangential ===
When you play with RGB addressable lights in electronics, you can get two types, RGB and RGBw.  (And sometimes the manufactures decide to follow different ordering protocols [GRBw] which makes the embedded-C programming even a bit more challenging.)  

The ability to create mixture of light by having 3 or 4 small LEDs light up is the basic function of how light emission works.  Here is a short video clip <https://www.youtube.com/watch?v=DBRJ0KbI1Hk> of an application, which was programmed in embedded C as part of a research grant to develop automated technologies to engage the mind and body of persons with Parkinson's disease <https://www.nsf.gov/awardsearch/showAward?AWD_ID=1819997>.  [We also had a nice punch-detection algorithm that would use the statistic called MAD to perform real-time signal processing.  Some details of how I used the Statistics of MAD is documented in an older "mastery" notebook.]

Obviously, the color schema presented herein is a function of light emission (which is how computers operate) and the aesthetics would be different for a paint-schema for color, as that is a function of how light reflects off a tangible surface.


### dechex (dec2hex)
Convert a number (technically an integer, don't know why they call it decimal, I guess it means base 10) to a hexadecimal.
```{r}
###### R::humanVerse #####
dechex(204);
```
I wrote the function to allow for mistakes with the integer thing.
```{r}
###### R::humanVerse #####
dechex(204.33);
```
It works for any size, I just use a 2-digit as that is what we need for colors.
```{r}
###### R::humanVerse #####
dechex(123456789, 1234);
```
```{r}
###### R::humanVerse #####
dechex(c(123456789, 1234));
```


Here is the entire range.
```{r}
###### R::humanVerse #####
dechex( 0:255);
```

### hexdec (hex2dec)
This is the inverse function, converts from hexadecimal string to a base-10 integer.
```{r}
###### R::humanVerse #####
hexdec("CC");
cat("\n", "===============", "\n\n");
dechex( hexdec("CC") );
cat("\n", "===============", "\n\n");
hexdec( dechex( hexdec("CC") ) );
cat("\n", "===============", "\n\n");
dechex( hexdec( dechex( hexdec("CC") ) ) );
```

```{r}
###### R::humanVerse #####
hexdec("Albuquerque");
```

### hex2rgb
The base format in my code is an RGB vector.  I can convert color in different formats, but the HEX and RGB are the basic engines.

```{r}
###### R::humanVerse #####
hex2rgb("Albuquerque");
```

You are supposed to pass in an HEXADECIMAL VALUE.
#### = WSU COLORS =
```{r}
# https://brand.wsu.edu/visual/colors/
wsu.crimson = "#981e32";
wsu.gray    = "#717171";
```

```{r}
###### R::humanVerse #####
hex2rgb( wsu.crimson );
```
You can unlist and simplify the result.

```{r}
# https://brand.wsu.edu/visual/colors/
wsu.crimson = "#981e32";
wsu.gray    = "#717171";

###### R::humanVerse #####
hex2rgb( wsu.crimson );
cat("\n", "===============", "\n\n");
unlist ( hex2rgb( wsu.crimson ) )
cat("\n", "===============", "\n\n");
as.integer( unlist ( hex2rgb( wsu.crimson ) ) );
```

```{r}
###### R::humanVerse #####
hex2rgb( wsu.gray );
cat("\n", "===============", "\n\n");
unlist ( hex2rgb( wsu.gray ) )
cat("\n", "===============", "\n\n");
as.integer( unlist ( hex2rgb( wsu.gray ) ) );
```

### rgb2hex
Of course, we need to be able to reverse it.
```{r}
###### R::humanVerse #####
rgb = hex2rgb( wsu.crimson );
rgb = cleanupRGB(rgb);
rgb;
cat("\n", "===============", "\n\n");
rgb2hex(rgb);
```

```{r}
###### R::humanVerse #####
rgb = hex2rgb( wsu.gray );
rgb = cleanupRGB(rgb);
rgb;
cat("\n", "===============", "\n\n");
rgb2hex(rgb);
```

## Other conversions
In color theory, there are other color formats.  RGB we normally associate with color emitted from light.  CMYK: (C)yam, (M)agenta, (Y)ellow, Blac(k) we normally associate with printing (printer cartridges).  Other formats include HSL / HSV which are useful for picking "harmonious colors" on the "color wheel".

To minimize the number of conversion functions, everything that is converted anchors to RGB.

### CMYK:  rgb2cmyk and cmyk2rgb
Notice, we may get some "rounding" error.  Or it could be a bug.
```{r}
###### R::humanVerse #####
(rgb = unlist ( hex2rgb( wsu.crimson ) ) );
cat("\n", "===============", "\n\n");
(cmyk = unlist( rgb2cmyk(rgb) ) );
cat("\n", "===============", "\n\n");
unlist ( cmyk2rgb( cmyk ) );
```

### HSL:  rgb2hsl and hsl2rgb
Notice, we may get some "rounding" error.  Or it could be a bug.  This one seems to be a "rounding" error.
```{r}
###### R::humanVerse #####
(rgb = unlist ( hex2rgb( wsu.crimson ) ) );
cat("\n", "===============", "\n\n");
(hsl = unlist(rgb2hsl(rgb) ) );
cat("\n", "===============", "\n\n");
unlist ( hsl2rgb( hsl ) );
```

### HSV:  rgb2hsv and hsv2rgb
Notice, we may get some "rounding" error.  Or it could be a bug.
HSV and HSL are very similar.  They will create slightly different results, as two lines of code are different in the formulas.  This one seems to be a "bug" (TODO).
```{r}
###### R::humanVerse #####
(rgb = unlist ( hex2rgb( wsu.crimson ) ) );
cat("\n", "===============", "\n\n");
(hsv = unlist(rgb2hsv(rgb) ) );
cat("\n", "===============", "\n\n");
unlist ( hsv2rgb( hsv ) );
```

## = Helper functions =
Above are the "engine functions" to make the color functions operate.  One layer up are "helper functions" to enable you to do stuff.  If you have other ideas for a "helper function", please share.

Remember it is about "git R done!"

### Random Color
```{r}
###### R::humanVerse #####
(rgb = unlist ( color.randomRGB() ) );
```

```{r}
###### R::humanVerse #####
(rgb = unlist ( color.randomRGB(key="key.to.remember.seed") ) );
```


```{r}
###### R::humanVerse #####
(hex = color.randomHEX() ) ;
```

```{r}
###### R::humanVerse #####
(hex = color.randomHEX(3, key="another.memory") ) ;
```
To access the "remembered" seeds, use the following:

```{r}
key = "another.memory";
.humanVerse[["colors"]][["random"]][[key]];
```
We generated 3 rgb colors and need 3 seeds for each: r,g,b ... so we had to store 9 different seeds.

### Opacity
RGB has a relationship to RGBa where the (a)lpha represents an opacity of the color based on some background (default: white).  So I wrote a function `color.setOpacity` where opacity is [0,100].  100% would be its full color capability.  It is anchored to `R::base` so it is using "hexadecimal" as its input.  It will render internally well on graphics.

```{r}
###### R::humanVerse #####
wsu.crimson.50 = color.setOpacity(wsu.crimson, 50);
  # this function assumes we have a well-formed HEX vector


# This RGBa format (HEX form): #981e3280  
#   ... is about equal to HEX: #cb8e98
# hex2rgb(wsu.crimson)    ... 152  30  50
# hex2rgb(wsu.crimson.50) ... 203 142 152
# IT APPEARS TO BE BLENDING WITH WHITE
#  +15 EASTER EGG:  write a function that 
#       converts #981e3280 to #cb8e98 [ hexdec(80) = 128 ... 50% is 128/255 colors]
#        AND
#       write its inverse function #cb8e98 => #981e3280 where the opacity = 50 would have to be passed into the function 
# THE OPACITY on BLACK WENT FROM #000000 [0,0,0] to #7F7F7F [127, 127, 127] ... it now looks gray, almost wsu.gray: #717171 [113, 113, 113] ... so what is the exact opacity % for WSU gray from black?

str = '
      <TABLE width=500 border=1 style="color: black; background-color: white;">
        <TR>
          <TH>CRIMSON</TH>
          <TD valign="middle" align="center"> 100% </TD>
          <TD align="center">{wsu.crimson}</TD>
        </TR>
        <TR>
          <TD colspan=3 style="background-color: {wsu.crimson}; opacity: 1.0; text-align: center;"> WSU COUGARS </TD>
        </TR>
        <TR>
          <TH>CRIMSON</TH>
          <TD valign="middle" align="center"> 50% </TD>
          <TD align="center">{wsu.crimson.50} =?= #cb8e98</TD>
        </TR>
        <TR>
          <TD colspan=3 style="background-color: {wsu.crimson}; opacity: 0.50; text-align: right;"> WSU COUGARS </TD>
        </TR>
      </TABLE>
      ';

str = str_replace( "{wsu.crimson.50}", wsu.crimson.50, str);
str = str_replace( "{wsu.crimson}", wsu.crimson, str);

cat(str);
castStringAsHTML(str);
```

 
### Web-safe
"In my day", the web had 216 colors, so we had to round colors down to these choices.
```{r}
###### R::humanVerse #####
wsu.crimson;
cat("\n", "===============", "\n\n");
(rgb = unlist ( hex2rgb( wsu.crimson ) ) );
cat("\n", "===============", "\n\n");
color.webSafeHEX(rgb);
```
```{r}
###### R::humanVerse #####
wsu.gray;
cat("\n", "===============", "\n\n");
(rgb = unlist ( hex2rgb( wsu.gray ) ) );
cat("\n", "===============", "\n\n");
color.webSafeHEX(rgb);
```

Based on that property, I wrote a generic `color.roundHEX` that will help prettify results, such as my rounding error in the section above.  It is a work in progress, which means "definitely buggy" ... `color.roundHEX ( hsl2rgb( hsl ), 1 );`

### Color Chromatics
Chromatics means shades of white, black and gray.  It is a gradient of the input color to white AND black respectively.  I did not port my old `C-based` code, but rather am plugging into `R::base` to make this simple.


```{r}
###### R::humanVerse #####
###### humanVerse::color.chromatics
wsu.crimson;
cat("\n", "===============", "\n\n");
(rgb = unlist ( hex2rgb( wsu.crimson ) ) );
cat("\n", "===============", "\n\n");
(wsu.chromatics = color.chromatics(rgb) );
cat("\n", "===============", "\n\n");
(wsu.chromatics.6 = color.chromatics(rgb, 6) );

# EASTER + 10:  There is a way to manipulate how RStudio "plugs in"
#  and prints a dataframe like below.  Figure out how to "colorize"
#  this dataframe so one of the columns has a background color of 
#  the hex.color value
#  e.g., `df = color.chromatics(rgb, 6); df$color.me = df$index;1
#         somehow make the `color.me` column have the 
#         background-color of df$hex.color
```

For simplicity, I am choosing, by default "6" colors on the way to white, and "6" colors on the way to black.

I can print as a static image, but that is not as cool (and you can't copy/paste).

```{r}
###### R::humanVerse #####
###### humanVerse::color.displayColorOptions
color.displayColorOptions(wsu.chromatics.6$hex.color);
```

### Colors in Gradient

`R::base` has a nice color gradient feature with some quirky syntax, so I cleaned it up a bit.

#### (rgb2col)


`R::base` has a nice function `col2rgb` ... yet does not have the inverse function `rgb2col` (ARGH!); the `col` represents a COLOR (name), a HEX (RGB) or a HEX (RGBa).  

It is bad software design to not have an obvious inverse function, so I wrote one.  It is included in my `functions-colors.R` file.

```{r}
###### R::humanVerse #####
rgb2col = function(x)
  {
  # reverses col2rgb function in ###### R::base #####
  x.n = dim(x)[1];
  if(x.n == 4)
    {
    x.rgb = t(x[1:4,]) /255;
    grDevices::rgb(   as.numeric(x.rgb[,1]),
                      as.numeric(x.rgb[,2]),
                      as.numeric(x.rgb[,3]),
                      as.numeric(x.rgb[,4]),
      names=rownames(x.rgb) );
    } else {
            x.rgb = t(x[1:3,]) /255;
            grDevices::rgb( x.rgb, names=rownames(x.rgb) );
            }
  }
```


```{r}
###### R::base #####
###### R::humanVerse #####
###### humanVerse::color.colorsInGradient
(wsu.gradient = color.colorsInGradient(10, 
                    c( wsu.crimson,wsu.gray)  ) );


color.displayColorOptions(wsu.gradient);

# (wsu.gradient = color.colorsInGradient(10, 
#                     c( rgb2hex( col2rgb(wsu.crimson) ),
#                        rgb2hex( col2rgb(wsu.gray)  ) ) ) );
```

### Color Grays

`R::base` has a built-in function to display a gradient of grays.

See <http://applied-r.com/grey-scales/> for an example. 


```{r}
###### R::base #####
(my.grays = gray.colors(12, start = 0, end = 1, gamma = 1) );

color.displayColorOptions(my.grays);

## gamma changes the output significantly.  

```
The above is a bit different than colors in gradient.

```{r}
###### R::humanVerse #####
(my.grays.2 = color.colorsInGradient(12, 
                    c( "black", "white")  ) );


color.displayColorOptions(my.grays.2);
```


### Color Wheel
There are traditionally 12 colors on the color wheel, every 30 degrees of the circle.

```{r}
library(plotrix);
###### R::humanVerse #####
color.plotWheel();  # pass in a flag to include "nearest name"
```


```{r}
###### R::humanVerse #####
wsu.crimson;
cat("\n", "===============", "\n\n");
(rgb = unlist ( hex2rgb( wsu.crimson ) ) );
cat("\n", "===============", "\n\n");
(wsu.wheel = color.buildWheel(rgb) );
```
There is a complement, split-complement, split, triad, square, rectangle, and so on.  There are just in reference to the focal color on the wheel.

```{r}
###### R::humanVerse #####
color.displayColorOptions(wsu.wheel$hex.color);
```
```{r}
###### R::humanVerse #####
color.plotWheel(wsu.wheel);  # pass in a flag to include "nearest name"
```

# Color Features (R::base)

`R::base` has good color features built in. 

## Get colors by name

```{r}
###### R::base #####
(all.colors = colors() );
```

```{r}
###### R::base #####
(unique.colors = colors(TRUE) );  # removes "duplicates" ... two names with same 
```  

```{r}
###### R::base #####
setdiff(all.colors, unique.colors);
```  


## Data Frame: COLOR, HEX, R,G,B

I have written a function that will be a dataframe of colors with name, HEX, and RGB.

```{r}
###### R::humanVerse #####
color.buildTable(unique.colors);
# Wouldn't that EASTER EGG above be a nice way to display this 
#   as a reference!
```

## Search by color name (wildcard)

```{r}
color.nameSearch("*blue*");
```


## Find color from HEX
Using some multivariate statistics, I can compute the nearest name(s) of a color by inputing its hex.

This function looks for an exact match and returns it, or returns `how.many` based on some distance metric (difference, distance, cosine similarity).

```{r}
###### R::humanVerse #####
( wsu.crimson.neighbors = color.findNearestName( wsu.crimson, 10, how="difference" ) );
color.displayColorOptions( c(wsu.crimson.neighbors, rep(wsu.crimson,10)),
                                                  showHEX = TRUE);
```

```{r}
###### R::humanVerse #####
( wsu.crimson.neighbors = color.findNearestName( wsu.crimson, 10, how="distance" ) );
color.displayColorOptions( c(wsu.crimson.neighbors, rep(wsu.crimson,10)),
                                                  showHEX = TRUE);
```


```{r}
###### R::humanVerse #####
( wsu.crimson.neighbors = color.findNearestName( wsu.crimson, 10, how="cosine" ) );
color.displayColorOptions( c(wsu.crimson.neighbors, rep(wsu.crimson,10) ),
                                                  showHEX = TRUE);
```

`how="distance"` seems to be the "best" based on accuracy/speed, although `how="cosine"` may be slightly better on accuracy.  I need to see if I can write my own function to replace the library and speed this method up.

```{r}
###### R::humanVerse #####
( wsu.gray.neighbors = color.findNearestName( wsu.gray, 10, how="distance" ) );
color.displayColorOptions( c(wsu.gray.neighbors, rep(wsu.gray,10)),
                                                  showHEX = TRUE);
```


## Built-in Palettes
`R::base` has a lot of color choices.

### `rainbow`

The code below generates 40 contiguous colors using the `?rainbow` function.  These values are hexadecimal RGB format <https://www.w3schools.com/colors/colors_hexadecimal.asp>.
```{r}
###### R::base #####
colors.rainbow = rainbow(40, s = 0.6, v = 0.75);
###### R::humanVerse #####
  color.displayColorOptions(colors.rainbow, ncol=4);
```



#### Transparency: `rainbow`

The true RGB color has another element appended, "alpha transparency" also in hexadecimal form, providing a RGBa color <https://www.w3schools.com/Css/css_colors_rgb.asp>.

```{r}
###### R::base #####
colors.rainbow = rainbow(40, s = 0.6, v = 0.75,
                      alpha=0.5);
###### R::humanVerse #####
  color.displayColorOptions(colors.rainbow, ncol=4);
```



### `heat.colors`

The code below generates 40 contiguous colors using the `?heat.colors` function.  

```{r}
###### R::base #####
colors.heat.colors = heat.colors(40);
###### R::humanVerse #####
  color.displayColorOptions(colors.heat.colors, ncol=4);
```

#### Transparency: `heat.colors`

The code below generates 40 contiguous colors using the `?heat.colors` function.  

```{r}
###### R::base #####
colors.heat.colors = heat.colors(40, alpha=0.5);
###### R::humanVerse #####
  color.displayColorOptions(colors.heat.colors, ncol=4);
```



### `terrain.colors`

The code below generates 40 contiguous colors using the `?terrain.colors` function.  

```{r}
###### R::base #####
colors.terrain.colors = terrain.colors(40);
###### R::humanVerse #####
  color.displayColorOptions(colors.terrain.colors, ncol=4);
```


#### Transparency: `terrain.colors`

The code below generates 40 contiguous colors using the `?terrain.colors` function.  

```{r}
###### R::base #####
colors.terrain.colors = terrain.colors(40, alpha=0.5);
###### R::humanVerse #####
  color.displayColorOptions(colors.terrain.colors, ncol=4);
```



### `topo.colors`

The code below generates 40 contiguous colors using the `?topo.colors` function.  

```{r}
###### R::base #####
colors.topo.colors = topo.colors(40);
###### R::humanVerse #####
  color.displayColorOptions(colors.topo.colors, ncol=4);
```


#### Transparency: `topo.colors`

The code below generates 40 contiguous colors using the `?topo.colors` function.  

```{r}
###### R::base #####
colors.topo.colors = topo.colors(40, alpha=0.5);
###### R::humanVerse #####
  color.displayColorOptions(colors.topo.colors, ncol=4);
```


### `cm.colors`

The code below generates 40 contiguous colors using the `?cm.colors` function.  

```{r}
###### R::base #####
colors.cm.colors = cm.colors(40);
###### R::humanVerse #####
  color.displayColorOptions(colors.cm.colors, ncol=4);
```


#### Transparency: `cm.colors`

The code below generates 40 contiguous colors using the `?cm.colors` function.  

```{r}
###### R::base #####
colors.cm.colors = cm.colors(40, alpha=0.5);
###### R::humanVerse #####
  color.displayColorOptions(colors.cm.colors, ncol=4);
```


























## More Palettes (`hcl.colors`)

```{r}
plotPalettes = FALSE;   # set TRUE to build graphics
                        # Rendered with TRUE, is 48 MB [Knit to HTML]
###### R::base #####
hcl.palette.list = hcl.pals();

as.data.frame( hcl.palette.list );

for(i in 1:length(hcl.palette.list))
  {
  hcl = hcl.palette.list[i];
  colors.hcl.colors = hcl.colors(40, palette=hcl);
  
  print(paste0("Palette: ", hcl));
  
###### R::humanVerse #####
  if(plotPalettes)
    {
    color.displayColorOptions(colors.hcl.colors, ncol=4);
    }
  print(paste0("   ---> alpha: ", 0.5));
  colors.hcl.colors = hcl.colors(40, palette=hcl,
                                        alpha=0.5);
###### R::humanVerse #####
  if(plotPalettes)
    {
    color.displayColorOptions(colors.hcl.colors, ncol=4);
    }
  }



```

# Conclusion

Online, you can read about all these special/cool palettes developed by others libraries (e.g.,  "RColorBrewer" or "wesanderson").  There is nothing new or novel in these libraries.  RGB and specifically RGBa are how colors are built in R (and in most user interfaces).  You can do some research, and build your own palette using the information contained herein.  The "pretty colors" are often a function of an "alpha" level of RGBa.  And it is related to the psychological perceptions we have as to why the color is "pretty".

## Build Your Own
Here is me showing the official brand colors for WSU as a custom list.  A few of the colors, UGH!
```{r}
# build a custom palette ...
# https://brand.wsu.edu/visual/colors/

colors.list = list();
colors.list[["monte_shaffer@wsu.edu"]] = list();

colors.list[["monte_shaffer@wsu.edu"]][["crimson"]] = "#981e32";
colors.list[["monte_shaffer@wsu.edu"]][["crimson-accent"]] = "#c60c30";
colors.list[["monte_shaffer@wsu.edu"]][["gray"]] = "#5e6a71";
colors.list[["monte_shaffer@wsu.edu"]][["gray-darker1"]] = "#464e54";
colors.list[["monte_shaffer@wsu.edu"]][["gray-darker2"]] = "#2a3033";
colors.list[["monte_shaffer@wsu.edu"]][["gray-black"]] = "#000000";
colors.list[["monte_shaffer@wsu.edu"]][["gray-lighter1"]] = "#8d959a";
colors.list[["monte_shaffer@wsu.edu"]][["gray-lighter2"]] = "#b5babe";
colors.list[["monte_shaffer@wsu.edu"]][["gray-lighter3"]] = "#d7dadb";
colors.list[["monte_shaffer@wsu.edu"]][["gray-lighter4"]] = "#eff0f1";
colors.list[["monte_shaffer@wsu.edu"]][["gray-white"]] = "#FFFFFF";
colors.list[["monte_shaffer@wsu.edu"]][["gray-lighter1"]] = "#8d959a";


colors.list[["monte_shaffer@wsu.edu"]][["orange"]] = "#b67233";
colors.list[["monte_shaffer@wsu.edu"]][["orange-accent"]] = "#f6861f";

colors.list[["monte_shaffer@wsu.edu"]][["green"]] = "#8f7e35";
colors.list[["monte_shaffer@wsu.edu"]][["green-accent"]] = "#ada400";

colors.list[["monte_shaffer@wsu.edu"]][["blue"]] = "#4f868e";
colors.list[["monte_shaffer@wsu.edu"]][["blue-accent"]] = "#00a5bd";

colors.list[["monte_shaffer@wsu.edu"]][["yellow"]] = "#c69214";
colors.list[["monte_shaffer@wsu.edu"]][["yellow-accent"]] = "#ffb81c";

# to practice, build out your own color scheme ... 
mycolors = unlist(colors.list$`monte_shaffer@wsu.edu`);
color.displayColorOptions(mycolors, showHEX=TRUE, ncol=2);
```


## TODO list

- Build some palette manager with a memory to make the visualization process more meaningful.
- Build an JSON import of a color dictionary using `library(rjson);`
- Import the "RColorBrewer" and "wesanderson" palettes using this JSON import option.  HOST JSON files on Github
- Easter Eggs are obvious TODOs.




