---
title: "R Notebook: Hello Friend"
output: html_notebook
---

# Hello Friend
This notebook will do a basic walkthrough on how to get up-and-running on the humanVerse.

## Welcome to R::humanVerse
The `humanVerse` is `R-base` friendly, very few dependencies here.  The objective is to make `R` more accessible by evolving its language to align with `C-based` standards.  I program in several C-based languages, and I want to minimize my `cognitive load` while maximizing my efficiency.  A few wrapper functions will make that so.

## include-setup.R

This one file has all the basic functions we need to load more functions or (of course) you can load the library.  

There are `misc` functions outside the library that run content-specific activities that do not belong in the main library as they include a lot of extraneous libraries.  For example, `functions-nlp.R` is well worth your time, please check it out.

### source setup
```{r}
github.monte.raw = "https://raw.githubusercontent.com/MonteShaffer/";
include.setup = paste0(github.monte.raw, "humanVerse/main/include.setup.R");
source(include.setup);
```

### source humanVerse
```{r}
github.monte.http = "https://github.com/MonteShaffer/";

github.monte.humanVerse = paste0(github.monte.http, "humanVerse/tree/main/humanVerse/R/"); # we will parse this page to get a list of the .R functions to include 

# includeGithubFolder(github.monte.humanVerse); # you can pass flag `force.download = TRUE` if you want to make certain it is not coming from cache

includeGithubFolder(github.monte.humanVerse, force.download = TRUE);
```

### source misc
```{r}
github.monte.misc = paste0(github.monte.http, "humanVerse/tree/main/misc/");  # we will parse this page to get a list of the .R functions to include 

includeGithubFolder(github.monte.misc); # you can pass flag `force.download = TRUE` if you want to make certain it is not coming from cache
```




