---
title: "R Notebook"
output: html_notebook
---

# INCLUDE

## HELPER
```{r}

setAttribute = function(myAttribute, myValue, myObj)
	{
	attributes(myObj)[[myAttribute]] = myValue;
	myObj;  # no object referencing, so I must return
	}

# stats.median
doMedian = function(x, type=1)
  {
  xx = stats::na.omit(x);
  as.numeric(stats::quantile(xx, prob=c(0.5), type=type));
  }



benchmark.efficiency = function(mb.res, digits=5)
	{
	mb.names = levels(mb.res$expr);
	
	out = NULL;

	A.name 		= mb.names[1];
	A 			= subset(mb.res, expr==A.name)$time;
	A.median 	= doMedian(A);

	# nano is 10^-9
	row = c(1,A.name,A.median, signif(A.median / 10^9, digits), 0); # BENCHMARK, delta efficiency is 0
	out = rbind(out, row);

	n.names = length(mb.names);
	if(n.names > 1)
		{
		for(i in 2:n.names)
			{
			B.name 		= mb.names[i];
			B 			= subset(mb.res, expr==B.name)$time;
			B.median 	= doMedian(B);
	
			B.eff 		= round(100* (A.median-B.median)/A.median , 2);

			row = c(i,B.name,B.median,signif(B.median / 10^9, digits),B.eff);
			out = rbind(out, row);
			}
		}

	out = data.frame(out);
	colnames(out)=c("Index","Name","Median","Seconds", "Delta.Efficiency");
	# rownames(out)=out$Name;
	rownames(out) = NULL;
		out$Median = as.numeric(out$Median);
		out$Delta.Efficiency = as.numeric(out$Delta.Efficiency);
		#out$Ranking = order(out$Delta.Efficiency, decreasing=TRUE); # not to be confused with 'rank'
		out$Rank = rank(out$Median, ties="first");
	
	out = setAttribute("microbenchmark.unit",.Options$microbenchmark.unit,out);
		
	out;
	}

md5.object = function(list)
	{
	str = listToString(list);
	md5(str);	
	}

```

## LIBRARY
```{r}

library(HVcpp);
Rcpp::sourceCpp("C:\\_git_\\github\\MonteShaffer\\humanVerse\\HVcpp\\src\\str.cpp");


functions.cleanKey = function(key, n=1)
	{
	substr(tolower(key),1,n);
	}

str.tolower = function(str, method="cpp", locale="en_US.UTF-8")
	{
# l10n_info();      # NON-TRIVIAL
# Sys.getlocale();
# stri_trans_tolower(string, locale = locale)

	# necessary overhead
	m = functions.cleanKey(method, 1);

	if(m == "s" && isTRUE(requireNamespace("stringi", quietly = TRUE)) )
		{		
		return ( stringi::stri_trans_tolower(str, locale) );
		}

	if(m == "c" && exists("cpp_strtolower"))
		{
		return( cpp_strtolower(str) );
		} 


	tolower(str);
	}


```

# BENCHMARK 'str.tolower'

## Use Case
```{r}
str_ = c(" jdfldDFLKJLKDSJdasj djslkfDFJK j     ", "KDkdolaDK") ;

A = cpp_strtolower(str_);
B = str.tolower(str_);
C = tolower(str_);
D = s_tolower(str_[1]);

stopifnot( identical(A,B) );
stopifnot( identical(A,C) );
stopifnot( identical(A[1],D) );

```


## MB
```{r}

str = rep(str_, 25);
# str = str[1];  # s_tolower(str),


# The available units are nanoseconds ("ns"), microseconds ("us"), milliseconds ("ms"), seconds ("s") and evaluations per seconds ("eps") and relative runtime compared to the best median time ("relative").
#.Options$microbenchmark.unit = "eps";
options(microbenchmark.unit="ns");

mb.res = microbenchmark::microbenchmark(
                                        
                                        stringi::stri_trans_tolower(str),
                                        tolower(str),
                                        cpp_strtolower(str),
                                        str.tolower(str),
                                        stringr::str_to_lower(str),
                                        str.tolower(str, "stringi"),
                                        str.tolower(str, "base"),
                                        
                                        
                                        
                                        times=1000,
                                        control=list("order"="random","warmup"=10)
                                        );

mb.res = setAttribute("microbenchmark.unit",as.character(options("microbenchmark.unit")),mb.res);

mb.res;
```

### boxplot
```{r}
boxplot(mb.res, horizontal=TRUE);
```

### efficiency
```{r}
mb.eff = benchmark.efficiency(mb.res);
mb.eff;
```

My C++ function is not performing well.  Why?



# BENCHMARK 'str.toupper'
```{r}

str.toupper = function(str, method="cpp", locale="en_US.UTF-8")
	{
	# necessary overhead
	m = functions.cleanKey(method, 1);

	if(m == "s" && isTRUE(requireNamespace("stringi", quietly = TRUE)) )
		{		
		return ( stringi::stri_trans_toupper(str, locale) );
		}

	if(m == "c" && exists("cpp_strtoupper"))
		{
		return( cpp_strtoupper(str) );
		} 

	toupper(str);
	}

```


## Use Case

```{r}
str_ = c(" jdfldDFLKJLKDSJdasj djslkfDFJK j     ", "KDkdolaDK") ;

A = cpp_strtoupper(str_);
B = stringi::stri_trans_toupper(str_);
C = toupper(str_);

stopifnot( identical(A,B) );
stopifnot( identical(A,C) );

```

## MB
```{r}

str = rep(str_, 25);


# The available units are nanoseconds ("ns"), microseconds ("us"), milliseconds ("ms"), seconds ("s") and evaluations per seconds ("eps") and relative runtime compared to the best median time ("relative").
#.Options$microbenchmark.unit = "eps";
options(microbenchmark.unit="ns");

mb.res = microbenchmark::microbenchmark(
                                        stringi::stri_trans_toupper(str),
                                        toupper(str),
                                        cpp_strtoupper(str),
                                        str.toupper(str),
                                        stringr::str_to_upper(str),
                                        str.toupper(str, "stringi"),
                                        str.toupper(str, "base"),
                                        
                                        
                                        times=1000,
                                        control=list("order"="random","warmup"=10)
                                        );

mb.res = setAttribute("microbenchmark.unit",as.character(options("microbenchmark.unit")),mb.res);

mb.res;
```

### boxplot
```{r}
boxplot(mb.res, horizontal=TRUE);
```

### efficiency
```{r}
mb.eff = benchmark.efficiency(mb.res);
mb.eff;
```

My C++ function is not performing well.  Why?




# BENCHMARK 'str.trim'
```{r}

str.trim = function(str, side="both", method="cpp", pattern="", ...)
  {
	# necessary overhead
	s = functions.cleanKey(side, 1);
	m = functions.cleanKey(method, 1);
	if(m == "c" && exists("cpp_trim"))
		{
		t = " \t\n\r\f\v";
		if(pattern != "") { t = pattern; }
		res = switch(s,
						  "l"  	= cpp_ltrim(str, t),
						  "r" 	= cpp_rtrim(str, t),
						  "b"  	= cpp_trim (str, t),
					cpp_trim(str, t)
					);
		return (res);
		}

	if(m == "s" && isTRUE(requireNamespace("stringi", quietly = TRUE)) )
		{
		p = "\\P{Wspace}";
		if(pattern != "") { p = pattern; }
		res = switch(s,
						  "l"	= stringi::stri_trim_left (str, p, ...),
						  "r" 	= stringi::stri_trim_right(str, p, ...),
						  "b"  	= stringi::stri_trim_both (str, p, ...),
					stringi::stri_trim_both(str, p, ...)
					);
		return (res);
		}
	
	g = "\\s+";
	if(pattern != "") { g = pattern; }
	res = switch(s,
						  "l" 	= gsub( paste0("^",g), "", str),
						  "r" 	= gsub( paste0(g,"$"), "", str),
						  "b"  	= gsub( paste0("^",g,"|",g,"$"), "", str),
                  gsub( paste0("^",g,"|",g,"$"), "", str)
                  );
    return (res);
	}

```


## Use Case

```{r}
str_ = c(" jdfldDFLKJLKDSJdasj djslkfDFJK j     ", "\n\t KDkdolaDK \n\r\n\t ") ;

A = cpp_trim(str_);
B = str.trim(str_, "both", "base");
C = stringi::stri_trim_both(str_);

stopifnot( identical(A,B) );
stopifnot( identical(A,C) );

```


## MB
```{r}

str = rep(str_, 25);


# The available units are nanoseconds ("ns"), microseconds ("us"), milliseconds ("ms"), seconds ("s") and evaluations per seconds ("eps") and relative runtime compared to the best median time ("relative").
#.Options$microbenchmark.unit = "eps";
options(microbenchmark.unit="ns");


mb.res = microbenchmark::microbenchmark(
                                        stringi::stri_trim_both(str),
                                        cpp_trim(str),
                                        str.trim(str, "both", "cpp"),
                                        str.trim(str, "both", "base"),
                                        stringr::str_trim(str),
                                        stringr::str_trim(str, "both"),
                                        str.trim(str, "both", "stringi"),
                                        
                                        
                                        times=1000,
                                        control=list("order"="random","warmup"=10)
                                        );

mb.res = setAttribute("microbenchmark.unit",as.character(options("microbenchmark.unit")),mb.res);

mb.res;
```

### boxplot
```{r}
boxplot(mb.res, horizontal=TRUE);
```

### efficiency
```{r}
mb.eff = benchmark.efficiency(mb.res);
mb.eff;
```

My C++ function is not performing well.  Why?  I have VECTORIZED them.


# BENCHMARK 'str.split'
```{r}
str.split = function(sep = " ", str = "hello friend", method="cpp", ...)
	{
	# necessary overhead
	m = functions.cleanKey(method, 1);

	if(m == "s" && isTRUE(requireNamespace("stringi", quietly = TRUE)) )
		{
		return (stringi::stri_split_fixed(str, sep, ...));
		}

	if(m == "c" && exists("cpp_explode"))
		{
		return( cpp_explode(sep, str) );
		}
	
	res = strsplit(str, sep, fixed=TRUE);
	res[[1]];
	}


```


## Use Case

```{r}
str_ = c("   jdfldDFLKJLKDSJdasj djslkfDFJK j", "   jdfldDFLKJLKDSJdasj djslkfDFJK j") ;
sep = " ";

A = cpp_explode(" ",str_)[[1]];
B = str.split(" ",str_, method="stringi", return.list=FALSE);
C = str.split(" ",str_, method="base", return.list=FALSE);

stopifnot( identical(A,B) );
stopifnot( identical(A,C) );

```


## MB
```{r}

str = str_;
sep = " ";


# The available units are nanoseconds ("ns"), microseconds ("us"), milliseconds ("ms"), seconds ("s") and evaluations per seconds ("eps") and relative runtime compared to the best median time ("relative").
#.Options$microbenchmark.unit = "eps";
options(microbenchmark.unit="ns");


mb.res = microbenchmark::microbenchmark(
                                        stringi::stri_split_fixed(str, sep),
                                        strsplit(str, sep, fixed=TRUE)[[1]],
                                        cpp_explode(sep,str),
                                        str.split(sep,str, "cpp"),
                                        str.split(sep,str, "base"),
                                        str.split(sep,str, "stringi"),
                                        
                                        
                                        times=10000,
                                        control=list("order"="random","warmup"=10)
                                        );

mb.res = setAttribute("microbenchmark.unit",as.character(options("microbenchmark.unit")),mb.res);

mb.res;
```

### boxplot
```{r}
boxplot(mb.res, horizontal=TRUE);
```

### efficiency
```{r}
mb.eff = benchmark.efficiency(mb.res);
mb.eff;
```

My C++ function is not performing well.  Why?  I have VECTORIZED them.



# BENCHMARK 'str.contains'
```{r}
str.contains = function(haystack = "hello friend", needle = " ", ...)
	{
	# grepl(needle, haystack, fixed = TRUE);
	tmp = str.split(needle, haystack);
	n = length(tmp);
	res = logical(n);
	for(i in 1:n)
		{
		res = if( length(tmp[[i]]) > 1 ) { TRUE } else { FALSE }
		}
	res;
	}


```


## Use Case

```{r}
haystack_ = c("   jdfldDFLKJLKDSJdasj djslkfDFJK j") ;
needle = " ";

A = str.contains(haystack_, needle, method="cpp");
B = str.contains(haystack_, needle, method="base");
C = grepl(needle, haystack_, fixed = TRUE);

stopifnot( identical(A,B) );
stopifnot( identical(A,C) );

```


## MB
```{r}

haystack = rep(haystack_, 5);
needle = " ";



# The available units are nanoseconds ("ns"), microseconds ("us"), milliseconds ("ms"), seconds ("s") and evaluations per seconds ("eps") and relative runtime compared to the best median time ("relative").
#.Options$microbenchmark.unit = "eps";
options(microbenchmark.unit="ns");


mb.res = microbenchmark::microbenchmark(
                                        grepl(needle, haystack, fixed = TRUE),
                                        is.substring(needle, haystack),
                                        str.contains(haystack, needle, method="cpp"),
                                        str.contains(haystack, needle, method="base"),
                                        str.contains(haystack, needle, method="stringi"),
                                        
                                        
                                        times=1000,
                                        control=list("order"="random","warmup"=10)
                                        );

mb.res = setAttribute("microbenchmark.unit",as.character(options("microbenchmark.unit")),mb.res);

mb.res;
```

### boxplot
```{r}
boxplot(mb.res, horizontal=TRUE);
```

### efficiency
```{r}
mb.eff = benchmark.efficiency(mb.res);
mb.eff;
```

My C++ function is not performing well.  Why?  I have VECTORIZED them.
